### 2017-02-28 2017mergingmerges/section/XX-Proof.tex
proof very rough

The system described here has some differences to our Coq formalisation.
First, the Coq formalisation has a separate @update@ instruction which modifies a variable in the local heap, rather than allowing heap updates in the output \Next~label of any instruction.
This causes the fusion definition to be slightly more complicated, as two output instructions must be emitted when performing a push or pull followed by an update.
This is a fairly minor difference, and we have made this change in the paper version for ease of exposition.
Ideally, a future version of the formalisation would include this change.
Secondly, our formalisation does not implement the concurrent evaluation semantics for processes, only sequential evaluation for a single process.
Instead we sequentially evaluate both processes separately with the same input values and outputs.

Despite these differences, we believe the Coq formalisation gives sufficient confidence in the correctness of the version presented here.

>>>>

\begin{code}
Theorem Soundness (P1 : Program L1 C V1) (P2 : Program L2 C V2) (ss : Streams) (h : Heap)
    (l1 : L1) (is1 : InputStates) (l2 : L2) (is2 : InputStates) :
  EvalBs (fuse P1 P2) ss h (LX l1 l2 is1 is2)
  -> EvalOriginal Var1 P1 P2 is1 ss h l1 /\ EvalOriginal Var2 P2 P1 is2 ss h l2.
\end{code}

The @Soundness@ theorem above uses @EvalBs@ to evaluate the fused program: if it evaluates to stream @ss@ and heap @h@, then @EvalOriginal@ ensures that the original program evaluates with that program's subset of the heap.

The system described here has some differences to our Coq formalisation.
First, the Coq formalisation has a separate @update@ instruction which modifies a variable in the local heap, rather than allowing heap updates in the output \Next~label of any instruction.
This causes the fusion definition to be slightly more complicated, as two output instructions must be emitted when performing a push or pull followed by an update.
This is a fairly minor difference, and we have made this change in the paper version for ease of exposition.
% Ideally, a future version of the formalisation would include this change.
Secondly, our formalisation does not implement the concurrent evaluation semantics for processes, only sequential evaluation for a single process.
Instead we sequentially evaluate both processes with the same input values and outputs.
Despite these differences, the Coq formalisation gives us sufficient confidence in the correctness of the version presented here.

### 2017-02-28 2017mergingmerges/section/XX-Related.tex
Kill commented out stuff in S1 S2 that we've already handled
proof very rough

This work aims to address the problems with existing combinator-based array fusion systems.
As stated in the introduction, neither pull-based or push-based fusion alone is sufficient.
Some combinators are inherently push-based, particularly those with multiple outputs such as @unzip@; while others are inherently pull-based, such as @zip@.

@@

>>>>

This work aims to address the problems with current combinator-based array fusion systems.
As stated in the introduction, neither pull-based or push-based fusion is sufficient.
Some combinators are inherently push-based, particularly those with multiple outputs such as @unzip@; while others are inherently pull-based, such as @zip@.

@@

% Recent work on stream fusion by \citet{kiselyov2016stream} uses staged computation to ensure all combinators are inlined, but for splits this causes excessive inlining which duplicates work, due to values of the source arrays being read multiple times.
